### 2017-11-30 MSDS_CaseStudy2_Master.Rmd
Jose and Lisa R files combined - Draft 1
We can begin working off this _Master file and merging into it.

---
title: "MSDS Case Study 2 - Procrastination and HDI Data"
author: "Jose Torres and Lisa Street"
date: "November 29, 2017"  
output:
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installing Necessary Libraries

Install necessary packages if not installed:

```{r custom packages}
if (!is.element("dplyr", installed.packages()[,1]))
  install.packages("dplyr",repos="http://cran.rstudio.com")
if (!is.element("ggplot2", installed.packages()[,1]))
  install.packages("ggplot2",repos="http://cran.rstudio.com")
if (!is.element("stringr", installed.packages()[,1]))
  install.packages("stringr",repos="http://cran.rstudio.com")
if (!is.element("rvest", installed.packages()[,1]))
  install.packages("rvest",repos="http://cran.rstudio.com")
if (!is.element("xml2", installed.packages()[,1]))
  install.packages("xml2",repos="http://cran.rstudio.com")
 if (!is.element("tidyr", installed.packages()[,1]))
  install.packages("tidyr",repos="http://cran.rstudio.com")
if (!is.element("curl", installed.packages()[,1]))
  install.packages("curl",repos="http://cran.rstudio.com")
if (!is.element("stargazer", installed.packages()[,1]))
  install.packages("stargazer",repos="http://cran.rstudio.com")
if (!is.element("stringi", installed.packages()[,1]))
  install.packages("stringi",repos="http://cran.rstudio.com")
```

```{r loadlibs, include=FALSE}

#Load libraries
library("dplyr")
library("rvest")
library("tidyr")
library("ggplot2")
library("stargazer")
library("ggpubr")
library("reshape2")
library("stringr")

```

## Load custom functions.

```{r custom functions}

#Custom functions for Case Study 2
#Last modified 11/26/17

#Wrapper function for gsub that maintains object classes
gsubkeep = function(pattern='',replacement=NA,x, ignore.case=FALSE, perl=FALSE,
										fixed=FALSE, useBytes=FALSE) {
	if (is.null(dim(x)) && !is.null(class(x))) {
		colObj = x
		colClass = class(colObj)
		colObj = gsub(pattern=pattern,replacement=replacement,x=colObj,
									ignore.case=ignore.case,perl=perl,fixed=fixed,
									useBytes=useBytes)
		if (colClass == 'factor') {
			colObj = as.factor(colObj)
		} else { 
			colObj = as(colObj,colClass) 
		}
		x = colObj
	} else {
		for (i in 1:length(x)) {
			colObj = x[,i]
			colClass = class(colObj)
			colObj = gsub(pattern=pattern,replacement=replacement,x=colObj,
										ignore.case=ignore.case,perl=perl,fixed=fixed,
										useBytes=useBytes)
			if (colClass == 'factor') {
				colObj = as.factor(colObj)
			} else { 
				colObj = as(colObj,colClass) 
			}
			x[,i] = colObj
		}
	}
	return(x)
}

#Function that row-stacks the identified columns of a list of data frames
#Parameters: {x: list of data frames, elements: the particular data frames within x to stack, 
#             cols: the particular columns to stack, colname: names of the columns selected with cols parameter }
list_rowbind = function(x,elements=1:length(x),cols = columns(1:length(x[[1]])),
												colname = colnames(x[[1]])[cols]) {
	result = data.frame()
	for (i in elements) {
		append_df = x[[i]][,cols]
		colnames(append_df) = colname
		result = bind_rows(result,append_df)
	}
	return(result)
}

#Function that creates a list of indices and corresponding strings which match keywords
#Paratermers: {x: a vector (to be coerced to character) to search, findtext: a vector of keywords to look for}
match_list = function(x,findtext='') {
	findtext = as.character(findtext)
	x = tolower(as.character(x))
	result = list(length(findtext))
	for (i in 1:length(findtext)) {
		result[i] = list(cbind('Idx'=grep(findtext[i],x),'Match'=x[grep(findtext[i],x)]))
	}
	return(result)
}

```

## Question 2: Read in and clean raw data

```{r Question2}

# 2: Read in and clean raw data

# 2A: Read in CSV
dataset_raw <- read.csv("C:\\SMU_INTRO_TO_DS\\CASESTUDY2\\Data\\Procrastination.csv")

dim(dataset_raw)
# There are 4264 rows and 61 columns in the procrastination dataset.

# 2B: Partition Procrastination into 2 tables (Attributes and Responses/Answers) and update column names
ID = 1:dim(dataset_raw)[1]
resp_attr = cbind(ID,dataset_raw[,1:14])
resp_answers = cbind(ID,dataset_raw[,15:length(dataset_raw)])

resp_attr_names = c('ID','Age','Gender','Kids','Edu','Work_Status',
										'Annual_Inc','Current_Occ','Employ_Yrs','Employ_Mths',
										'Comm_Size','Country_Res','Married','Num_sons',
										'Num_daught')

resp_answer_names = c('ID',paste('DP_',1:5,sep=''),paste('AIP_',1:15,sep=''),
											paste('GP_',1:20,sep=''),paste('SWLS_',1:5,sep=''),'Self_Score','Others_Score')

colnames(resp_attr) = resp_attr_names
colnames(resp_answers) = resp_answer_names

# 2C: Cleanup the data

# 2Ci through 2civ:

# Begin by converting all blank or empty strings to NA in the entire data set
resp_attr = gsubkeep(pattern='^$|^ $',replacement=NA,x=resp_attr)

# Now go through individual attributes list and replace 'bad' values with NA
cleanup_list = data.frame(rbind(c(' Kids$','',4), #remove 'Kids'
																c('0', NA, 6), #Work status
																c('0|please specify',NA,8), #Occupation 
																c('999',NA,9), #Employment Years
																c('[08]',NA,11), #Community Size
																c('0',NA,12), #Country of Residence
																c('0',NA,13), #Married
																c('Male','1',14), #Number of sons
																c('Female','2',14))) #Number of sons

# Employ_Yrs_num - replace small numbers with 0.  Round to nearest integer.
resp_attr[which(resp_attr[,9] < .5),9] = 0
resp_attr[,9] = as.integer(round(resp_attr[,9],digits=0))

# Num_sons_fac - Convert to numeric
resp_attr[,14] = as.integer(resp_attr[,14])

# Num_daughters_num - no change

# 2d:
# Set columns to the proper data types
for (i in 1:dim(cleanup_list)[1]) {
	pattern = as.character(cleanup_list[i,1])
	replacement = as.character(cleanup_list[i,2])
	column = as.integer(as.character(cleanup_list[i,3]))
	resp_attr[,column] = gsubkeep(pattern=pattern,replacement=replacement,x=resp_attr[,column])
}

# 2e:
# Assign mean columns for the 4 response categories
resp_answers$DP_Avg = round(apply(X=resp_answers[,2:6],MARGIN=1,FUN=mean),5)
resp_answers$AIP_Avg = round(apply(X=resp_answers[,7:21],MARGIN=1,FUN=mean),5)
resp_answers$GP_Avg = round(apply(X=resp_answers[,22:41],MARGIN=1,FUN=mean),5)
resp_answers$SWLS_Avg = round(apply(X=resp_answers[,42:46],MARGIN=1,FUN=mean),5)

```

## Question 3: HDI table scrape from Wikipedia

```{r Question3 HDI table scrape from Wikipedia}

# Scrape the Wikipedia website for the 8 HDI data tables

URL = 'https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index#Complete_list_of_countries'

html_resp = read_html(URL)

#HDI_data is a single data frame country and HDI
HDI_data = 
	html_nodes(html_resp,css='table.wikitable') %>%
	html_table(fill=TRUE) %>%
	list_rowbind(elements=c(1:8),cols=c(3,4),colname=c('Country','HDI'))

#Cleaning up HDI data and adding categories
HDI_data = subset(HDI_data,HDI_data[,1] != 'Change in rank from previous year[1]')
rownames(HDI_data) = 1:dim(HDI_data)[1]
HDI_data$HDI_Cat = c(rep('Very High',51),rep('High',56),rep('Medium',41),rep('Low',41))
HDI_data$HDI = as.numeric(HDI_data$HDI)

#Attach HDI data to attribute table, and maintain original row ordering
resp_attrwHDI = merge(x=resp_attr,y=HDI_data,by.x='Country_Res',by.y='Country',all.x=TRUE,incomparables=NA)
resp_attrwHDI = resp_attrwHDI[order(resp_attrwHDI$ID),]

```

# Question 4: Preliminary Analysis

```{r Question4 Preliminary Analysis}

# 4A:
# Remove respondents under 18 from resp_attr and resp_answers
row_keep = which(resp_attrwHDI$Age>=18)
resp_attrwHDI = resp_attrwHDI[row_keep,]
resp_answers = resp_answers[row_keep,]

#Merge attributes with question answers for analysis
resp_full = merge(x=resp_answers,y=resp_attrwHDI,by.x='ID',by.y='ID',all.y=TRUE)

# 4B:
#statistics table
stargazer(resp_full[,c('Age','Annual_Inc','HDI','DP_Avg','AIP_Avg','GP_Avg','SWLS_Avg')],type='text',
					summary.stat=c('n','min','p25','median','p75','max','mean','sd'))

#Create 4 plots for sample figure:

h1 = gghistogram(resp_full,x='Age',y='..count..',
								 bins=10,
								 fill='blue',
								 size=2,
								 title='Age',
								 color='white'
)

h1 + font('x.text',size=8)

h2 = gghistogram(resp_full,x='Annual_Inc',y='..count..',
								 bins=10,
								 fill='blueviolet',
								 size=2,
								 title='Ann Inc',
								 color='white'
)

h2 + font('x.text',size=10)

h3 = gghistogram(resp_full,x='HDI',y='..count..',
								 bins=5,
								 fill='cadetblue3',
								 size=2,
								 title='HDI',
								 color='white'
)

DPMetric <- resp_full["DP_Avg"]
DPMetric$Variable <- 'DP_Avg'
colnames(DPMetric) <- c("Value","Variable")

AIPMetric <- resp_full["AIP_Avg"]
AIPMetric$Variable <- 'AIP_Avg'
colnames(AIPMetric) <- c("Value","Variable")

GPMetric <- resp_full["GP_Avg"]
GPMetric$Variable <- 'GP_Avg'
colnames(GPMetric) <- c("Value","Variable")

SWLSMetric <- resp_full["SWLS_Avg"]
SWLSMetric$Variable <- 'SWLS_Avg'
colnames(SWLSMetric) <- c("Value","Variable")

metrics <- rbind(DPMetric, AIPMetric, GPMetric, SWLSMetric)

h4 = ggboxplot(metrics,x='Variable',
							 y='Value',
							 color='Variable',
							 palette='jco',
							 size=1.5
)

h4 + font('x.text',size=10)

ggarrange(ggarrange(h1,h2,h3,ncol=3,labels=c('1','2','3')),
					h4,
					nrow=2,
					labels='4')

# Neither the Age nor Annual Income histograms are particularly normally distributed.  The Age histogram is a bit of a bimodal
# distribution with peaks around the ages of 25, 45 and 55. THe Annual Income is more right-skewed.

# 4C:

#Categorize occupations for table

jobs = cbind(as.character(resp_full$Current_Occ), NA)

jobs_matrix = unlist(apply(jobs,MARGIN=2,FUN=function(x){strsplit(x,' ')})) %>%
	gsub(pattern='[[:punct:]]',replacement='') %>%
	gsub(pattern='^$|^ $',replacement=NA)

jobs_matrix = unlist(apply(jobs,MARGIN=2,FUN=function(x){strsplit(x,' ')})) %>%
	gsub(pattern='[[:punct:]]',replacement='') %>%
	gsub(pattern='^$|^ $',replacement=NA) %>%
	subset(!is.na(jobs_matrix))

jobs_matrix = as.factor(tolower(jobs_matrix))

jobs_count = as.data.frame(table(jobs_matrix))
colnames(jobs_count)=c('title','count')
jobs_count = jobs_count[order(jobs_count$count,jobs_count$title,decreasing=TRUE),]

#Get top 10 job keywords
keywords = jobs_count[1:10,]

keywords_del = c('and','of')
top10Jobs = subset(keywords,!keywords$title %in% keywords_del)

# Frequencies per column 
# Unique distributions
# Gender
apply(resp_full["Gender"], 2, table)

# WorkStatus
apply(resp_full["Work_Status"], 2, table)

#Distributions across Gender and Work Status
with(resp_full, table(Gender, Work_Status))

top10Jobs

# 4D:

# Counts of participants per country in descending order

countryCt <- count(resp_full, resp_full$Country_Res)
colnames(countryCt) <- c("Country", "Count")

sortedCC <- countryCt[order(countryCt$Count, decreasing = TRUE),]

print(sortedCC)

# 4E:

# Find the number of people whose self view matched others view

resp_full$Others_Score <- as.character(resp_full$Others_Score)
resp_full$Self_Score <- as.character(resp_full$Self_Score)

viewMatch <- count(resp_full[which(resp_full$Self_Score == resp_full$Others_Score),])
print(viewMatch)

```

## Question 5: Visualization and Deeper Analysis

```{r Question5 Preliminary Analysis}

# 5B:

DPMeanSub <- resp_full[,c("Country_Res","DP_Avg", "HDI_Cat")]
DPMeanAvg <- aggregate(DP_Avg~Country_Res, DPMeanSub, mean)
DPMeanUnique <- aggregate(HDI_Cat~Country_Res, DPMeanSub, unique)

DPMeanAvgHDI <- merge(DPMeanAvg, DPMeanUnique , by.x=c("Country_Res"),
											by.y=c("Country_Res"))

SortedDP <- DPMeanAvgHDI[order(DPMeanAvgHDI$DP_Avg, decreasing = TRUE),]
Top15DP <- SortedDP[1:15,]

##Set chunk size for output
ggplot(Top15DP, aes(reorder(Country_Res, -DP_Avg), DP_Avg))+
	geom_bar(aes(fill=HDI_Cat), stat="identity")+
	ggtitle("Countries with the top 15 DPMean") +
	theme(plot.title = element_text(hjust = 0.5)) +
	xlab("Country Name")+
	ylab("DP Mean Value")

####START HERE:

# 5C:
AIPMeanSub <- resp_full[,c("Country_Res","AIP_Avg", "HDI_Cat")]
AIPMeanAvg <- aggregate(AIP_Avg~Country_Res, AIPMeanSub, mean)
AIPMeanUnique <- aggregate(HDI_Cat~Country_Res, AIPMeanSub, unique)

AIPMeanAvgHDI <- merge(AIPMeanAvg, AIPMeanUnique , by.x=c("Country_Res"),
											 by.y=c("Country_Res"))

SortedAIP <- AIPMeanAvgHDI[order(AIPMeanAvgHDI$AIP_Avg, decreasing = TRUE),]
Top15AIP <- SortedAIP[1:15,]

##Set chunk size for output
ggplot(Top15AIP, aes(reorder(Country_Res, -AIP_Avg), AIP_Avg))+
	geom_bar(aes(fill=HDI_Cat), stat="identity")+
	ggtitle("Countries with the top 15 AIPMean") +
	theme(plot.title = element_text(hjust = 0.5)) +
	xlab("Country Name")+
	ylab("AIP Mean Value")

#Find countries that exist in both the top 15 AIP and DP Means
merge(Top15DP, Top15AIP, by.x=c("Country_Res"), by.y=c("Country_Res"))

# There are 6 countries that exist in both DP and API top 15 Means.  They are:
# Dominican Republic, Ecuador, Panama, Qatar, Sri Lanka, Uraguay

# 5D:

# Subset merged data frame to only include those rows where Gender is not empty and Annual Income is not empty
mDFMF <- subset(resp_full[c("Country_Res","Age","Annual_Inc","Gender")], Gender != "" & Annual_Inc != "")

# Get the average income per age
mDFMFAvg <- aggregate(Annual_Inc~Age + Gender, mDFMF, mean)

par(mar=c(4,6,2,2))
plot(mDFMFAvg$Annual_Inc ~ mDFMFAvg$Age, xaxt="n", yaxt="n", pch = 16, cex = 1.3, col = ifelse(mDFMFAvg$Gender == "Female", "hot pink", "blue"), xlab="", ylab="")
axis(1,at=pretty(mDFMFAvg$Age),labels=pretty(mDFMFAvg$Age),las=1)
axis(2,at=pretty(mDFMFAvg$Annual_Inc),labels=format(pretty(mDFMFAvg$Annual_Inc),big.mark=",", scientific=FALSE),las=1)
mtext(text="Age", side=1, line=2)
mtext(text="Annual Income", side=2, line=5)
title("Mean Income by Age and Gender")
abline(lm(mDFMFAvg$Annual_Inc ~ mDFMFAvg$Age), col = "green")

# There does seem to be a relationship between age and annual income, with annual income increasing with age.  However,
# there also seems to be a large disparity between males and females and their annual income starting at around age 40 and 
# growing from there.

# 5E:

# Subset merged data frame to only include those rows where Gender is not empty
mDFHDI <- subset(resp_full[c("Country_Res","SWLS_Avg", "HDI", "HDI_Cat")])

mDFHDIAvg <- aggregate(SWLS_Avg~HDI + HDI_Cat, mDFHDI, mean)

par(mar=c(4,6,2,2))
plot(mDFHDIAvg$SWLS_Avg ~ mDFHDIAvg$HDI, xaxt="n", yaxt="n", pch = 16, cex = 1.3, col = "blue", xlab="", ylab="")
axis(1,at=pretty(mDFHDIAvg$HDI),labels=pretty(mDFHDIAvg$HDI),las=1)
axis(2,at=pretty(mDFHDIAvg$SWLS_Avg),labels=format(pretty(mDFHDIAvg$SWLS_Avg),big.mark=",", scientific=FALSE),las=1)
mtext(text="HDI", side=1, line=2)
mtext(text="Mean Life Satisfaction", side=2, line=5)
title("Life Satisfaction Mean by HDI")
abline(lm(mDFHDIAvg$SWLS_Avg ~ mDFHDIAvg$HDI), col = "green")

# Barchart between HDI Category and Mean Life Satisfaction

ggplot(mDFHDIAvg, aes(fill=HDI_Cat, y=SWLS_Avg, x=HDI_Cat)) + 
	scale_x_discrete(labels=c("High Human Development" = "HHD", "Very High Human Development" = "VHHD",
														"Medium Human Development" = "MHD", "Low Human Development" = "LHD")) +
	geom_bar(position="dodge", stat="identity") +
	ggtitle("Mean Life Satisfaction per HDI Category Test") +
	theme(plot.title = element_text(hjust = 0.5)) +
	xlab("Human Development Category") +
	ylab("Life Satisfaction Mean")

```

### 2017-11-30 MSDS_CaseStudy2_Master.R

@@ -1,0 +1,381 @@
+# Install packages and libraries
+
+#install.packages("dyplr")
+#install.packages("rvest")
+#install.packages("xml2")
+#install.packages("tidyr")
+#install.packages("ggplot2")
+#install.packages("curl")
+#install.packages("stargazer")
+#install.packages("stringi")
+
+
+#Get libraries
+#library("dplyr")
+#library("rvest")
+#library("tidyr")
+#library("ggplot2")
+#library("stargazer")
+#library("ggpubr")
+#library("reshape2")
+#library("stringr")
+
+#Include custom function library
+source('CS2_Functions.R')
+
+# 2: Read in and clean raw data
+
+# 2A: Read in CSV
+dataset_raw <- read.csv("C:\\SMU_INTRO_TO_DS\\CASESTUDY2\\Data\\Procrastination.csv")
+
+dim(dataset_raw)
+# There are 4264 rows and 61 columns
+
+# 2B: Partition Procrastination into 2 tables (Attributes and Responses/Answers) and update column names
+ID = 1:dim(dataset_raw)[1]
+resp_attr = cbind(ID,dataset_raw[,1:14])
+resp_answers = cbind(ID,dataset_raw[,15:length(dataset_raw)])
+
+resp_attr_names = c('ID','Age','Gender','Kids','Edu','Work_Status',
+										'Annual_Inc','Current_Occ','Employ_Yrs','Employ_Mths',
+										'Comm_Size','Country_Res','Married','Num_sons',
+										'Num_daught')
+
+resp_answer_names = c('ID',paste('DP_',1:5,sep=''),paste('AIP_',1:15,sep=''),
+											paste('GP_',1:20,sep=''),paste('SWLS_',1:5,sep=''),'Self_Score','Others_Score')
+
+colnames(resp_attr) = resp_attr_names
+colnames(resp_answers) = resp_answer_names
+
+
+# 2C: Cleanup the data
+
+# 2Ci through 2civ:
+
+# Begin by converting all blank or empty strings to NA in the entire data set
+resp_attr = gsubkeep(pattern='^$|^ $',replacement=NA,x=resp_attr)
+
+
+# Now go through individual attributes list and replace 'bad' values with NA
[…]

### 2017-12-01 MSDS_CaseStudy2_Master.Rmd
Updated rmarkdown to fix some things as well as add the code necessary to have pretty tables

@@
   install.packages("stringi",repos="http://cran.rstudio.com")
+if (!is.element("scales", installed.packages()[,1]))
+  install.packages("scales",repos="http://cran.rstudio.com")
+if (!is.element("kableExtra", installed.packages()[,1]))
+  install.packages("kableExtra",repos="http://cran.rstudio.com")
+if (!is.element("knitr", installed.packages()[,1]))
+  install.packages("knitr",repos="http://cran.rstudio.com")
+
 ```
@@
 library("stringr")
+library("scales")
+library("knitr")
+library("kableExtra")
 
@@
 #Custom functions for Case Study 2
+#Please open MSDS6306_Final_Case_Study_Functions.R for more details
 #Last modified 11/26/17
 
-#Wrapper function for gsub that maintains object classes
-gsubkeep = function(pattern='',replacement=NA,x, ignore.case=FALSE, perl=FALSE,
-										fixed=FALSE, useBytes=FALSE) {
-	if (is.null(dim(x)) && !is.null(class(x))) {
-		colObj = x
-		colClass = class(colObj)
-		colObj = gsub(pattern=pattern,replacement=replacement,x=colObj,
-									ignore.case=ignore.case,perl=perl,fixed=fixed,
-									useBytes=useBytes)
-		if (colClass == 'factor') {
-			colObj = as.factor(colObj)
-		} else { 
-			colObj = as(colObj,colClass) 
-		}
-		x = colObj
-	} else {
-		for (i in 1:length(x)) {
-			colObj = x[,i]
-			colClass = class(colObj)
-			colObj = gsub(pattern=pattern,replacement=replacement,x=colObj,
-										ignore.case=ignore.case,perl=perl,fixed=fixed,
-										useBytes=useBytes)
-			if (colClass == 'factor') {
-				colObj = as.factor(colObj)
-			} else { 
-				colObj = as(colObj,colClass) 
-			}
-			x[,i] = colObj
-		}
-	}
-	return(x)
-}
-
-#Function that row-stacks the identified columns of a list of data frames
-#Parameters: {x: list of data frames, elements: the particular data frames within x to stack, 
-#             cols: the particular columns to stack, colname: names of the columns selected with cols parameter }
-list_rowbind = function(x,elements=1:length(x),cols = columns(1:length(x[[1]])),
-												colname = colnames(x[[1]])[cols]) {
-	result = data.frame()
-	for (i in elements) {
-		append_df = x[[i]][,cols]
-		colnames(append_df) = colname
-		result = bind_rows(result,append_df)
-	}
-	return(result)
-}
-
-#Function that creates a list of indices and corresponding strings which match keywords
-#Paratermers: {x: a vector (to be coerced to character) to search, findtext: a vector of keywords to look for}
-match_list = function(x,findtext='') {
-	findtext = as.character(findtext)
-	x = tolower(as.character(x))
-	result = list(length(findtext))
-	for (i in 1:length(findtext)) {
-		result[i] = list(cbind('Idx'=grep(findtext[i],x),'Match'=x[grep(findtext[i],x)]))
-	}
-	return(result)
-}
+source('MSDS6306_Final_Case_Study_Functions.R')
 
@@
 # 2A: Read in CSV
-dataset_raw <- read.csv("C:\\SMU_INTRO_TO_DS\\CASESTUDY2\\Data\\Procrastination.csv")
+filepath = 'C:\\Users\\Jose\\Downloads\\Case_Study_2\\CaseStudy2_MSDS'
+dataset_raw <- read.csv(paste(filepath,'Procrastination.csv',sep='\\'))
 
@@
 
-```{r Question4 Preliminary Analysis}
+```{r Question4 Preliminary Analysis, warning=FALSE}
 
@@
 #statistics table
-stargazer(resp_full[,c('Age','Annual_Inc','HDI','DP_Avg','AIP_Avg','GP_Avg','SWLS_Avg')],type='text',
-					summary.stat=c('n','min','p25','median','p75','max','mean','sd'))
+stargazer(resp_full[,c('Age','Annual_Inc','HDI','DP_Avg','AIP_Avg','GP_Avg','SWLS_Avg')],
+					summary.stat=c('n','min','p25','median','p75','max','mean','sd'),type='text')
 
@@
 								 size=2,
-								 title='Age',
-								 color='white'
+								 title='Histogram of Age',
+								 color='white',
+								 ylab='Count'
 )
 
-h1 + font('x.text',size=8)
+h1 = h1 + font('xy.text',size=12) + theme(plot.title=element_text(hjust=0.5))
 
 h2 = gghistogram(resp_full,x='Annual_Inc',y='..count..',
-								 bins=10,
 								 fill='blueviolet',
 								 size=2,
-								 title='Ann Inc',
-								 color='white'
+								 bins=25,
+								 title='Histogram of Annual Income',
+								 color='white',
+								 ylab='Count',
+								 xlab='Annual Income'
 )
 
-h2 + font('x.text',size=10)
+Annual_Inc_Clean = resp_full[which(!is.na(resp_full$Annual_Inc)),'Annual_Inc']
+
+h2 = h2 + font('xy.text',size=12) + 
+  theme(plot.title=element_text(hjust=0.5)) +
+  rotate_x_text(30) +
+  scale_x_continuous(label=dollar_format(),breaks = round(seq(min(Annual_Inc_Clean), max(Annual_Inc_Clean), by = 50000),1))
 
 h3 = gghistogram(resp_full,x='HDI',y='..count..',
-								 bins=5,
+								 bins=35,
 								 fill='cadetblue3',
 								 size=2,
-								 title='HDI',
-								 color='white'
+								 title='Histogram of HDI',
+								 color='white',
+								 ylab='Count'
 )
+
+h3 = h3 + font('xy.text',size=12) + theme(plot.title=element_text(hjust=0.5))
 
@@
 							 palette='jco',
-							 size=1.5
-)
+							 size=1,
+							 xlab='')
 
-h4 + font('x.text',size=10)
+h4 = h4 + font('xy.text',size=12) + theme(plot.title=element_text(hjust=0.5)) +
+  rotate_x_text(30)
 
-ggarrange(ggarrange(h1,h2,h3,ncol=3,labels=c('1','2','3')),
-					h4,
+ggarrange(h1,h3,
+					h2,h4,
 					nrow=2,
-					labels='4')
+					ncol=2)
 
@@
 
+#For the codebook only
+#These are the job assignments we subjectively made to get the top10 job counts shown:
+top_jobs = match_list(resp_full$Current_Occ,findtext=keywords$title)
+
+for (i in 1:length(top10Jobs$title)) {
+print(paste(tolower(as.character(top10Jobs$title[i])),'<-', unique(unique(top_jobs[[i]][,2]))))
+}
+
 # Frequencies per column 
 # Unique distributions
+
 # Gender
-apply(resp_full["Gender"], 2, table)
+gender_table = as.data.frame(table(resp_full$Gender))
+colnames(gender_table) = c('Gender','Count')
+kable(gender_table,row.names=FALSE,format='html')%>%
+  kable_styling(bootstrap_options='striped',full_width=FALSE)%>%
+  row_spec(row=1:dim(gender_table)[1],bold=T,color='white',background='darkred')
 
 # WorkStatus
-apply(resp_full["Work_Status"], 2, table)
+work_table = as.data.frame(table(resp_full$Work_Status))
+colnames(work_table) = c('Status','Count')
+work_table = work_table[order(work_table$Count,decreasing=TRUE),]
+kable(work_table,row.names=FALSE,format='html')%>%
+  kable_styling(bootstrap_options=c('striped','condensed'),full_width=FALSE)%>%
+  row_spec(row=1:dim(work_table)[1],bold=T,color='white',background='darkred')
 
 #Distributions across Gender and Work Status
-with(resp_full, table(Gender, Work_Status))
+genderwork_table = as.data.frame(table(resp_full$Gender,resp_full$Work_Status))
+colnames(genderwork_table) = c('Gender','Work_Status','Count')
+genderwork_table = genderwork_table[order(genderwork_table$Count,decreasing=TRUE),]
+kable(genderwork_table,row.names=FALSE,format='html')%>%
+  kable_styling(bootstrap_options='striped',full_width=FALSE)%>%
+  row_spec(row=1:dim(genderwork_table)[1],bold=T,color='white',background='darkred')
 
-top10Jobs
+kable(top10Jobs,row.names=FALSE,format='html')%>%
+  kable_styling(bootstrap_options='striped',full_width=FALSE)%>%
+  row_spec(row=1:dim(top10Jobs)[1],bold=T,color='white',background='darkred')
 
@@
 
-countryCt <- count(resp_full, resp_full$Country_Res)
-colnames(countryCt) <- c("Country", "Count")
-
-sortedCC <- countryCt[order(countryCt$Count, decreasing = TRUE),]
-
-print(sortedCC)
-
+countryCt = as.data.frame(table(resp_full$Country_Res))
+colnames(countryCt) = c('Country','Count')
+sortedCC = countryCt[order(countryCt$Count, decreasing = TRUE),]
+kable(head(sortedCC,20),row.names=FALSE,format='html')%>%
+  kable_styling(bootstrap_options='striped',full_width=FALSE)%>%
+  row_spec(row=1:20,bold=T,color='white',background='darkred')
 # 4E:
@@
 
-viewMatch <- count(resp_full[which(resp_full$Self_Score == resp_full$Others_Score),])
-print(viewMatch)
+match_yes = sum(resp_full$Self_Score == 'yes' & resp_full$Others_Score == 'yes')
+match_no = sum(resp_full$Self_Score == 'no' & resp_full$Others_Score == 'no')
+match_either = as.data.frame(cbind(match_yes,match_no))
+colnames(match_either) = c('Others Agree I Procrastinate','Others Agree I Do Not Procrastinate')
+kable(match_either,row.names=FALSE,format='html')%>%
+  kable_styling(bootstrap_options='striped',full_width=FALSE)%>%
+  row_spec(row=1:1,bold=T,color='black',background='beige')%>%
+  column_spec(1:2,width='1cm')
 

### 2017-12-01 MSDS_CaseStudy2_Master.R

@@ -8,6 +8,7 @@
 #install.packages("curl")
 #install.packages("stargazer")
 #install.packages("stringi")
+#install.packages("scales")
 
 
 #Get libraries
@@ -19,14 +20,16 @@
 #library("ggpubr")
 #library("reshape2")
 #library("stringr")
+#library("scales")
 
 #Include custom function library
-source('CS2_Functions.R')
+source('MSDS6306_Final_Case_Study_Functions.R')
 
 # 2: Read in and clean raw data
 
 # 2A: Read in CSV
-dataset_raw <- read.csv("C:\\SMU_INTRO_TO_DS\\CASESTUDY2\\Data\\Procrastination.csv")
+filepath = 'C:\\Users\\Jose\\Downloads\\Case_Study_2\\CaseStudy2_MSDS'
+dataset_raw <- read.csv(paste(filepath,'Procrastination.csv',sep='\\'))
 
 dim(dataset_raw)
 # There are 4264 rows and 61 columns
@@ -144,29 +147,41 @@ h1 = gghistogram(resp_full,x='Age',y='..count..',
 								 bins=10,
 								 fill='blue',
 								 size=2,
-								 title='Age',
-								 color='white'
+								 title='Histogram of Age',
+								 color='white',
+								 ylab='Count'
 )
 
-h1 + font('x.text',size=8)
+h1 = h1 + font('xy.text',size=12) + theme(plot.title=element_text(hjust=0.5))
+
 
 h2 = gghistogram(resp_full,x='Annual_Inc',y='..count..',
-								 bins=10,
 								 fill='blueviolet',
 								 size=2,
-								 title='Ann Inc',
-								 color='white'
+								 bins=25,
+								 title='Histogram of Annual Income',
+								 color='white',
+								 ylab='Count',
+								 xlab='Annual Income'
 )
 
-h2 + font('x.text',size=10)
+Annual_Inc_Clean = resp_full[which(!is.na(resp_full$Annual_Inc)),'Annual_Inc']
+
+h2 = h2 + font('xy.text',size=12) + 
+  theme(plot.title=element_text(hjust=0.5)) +
+  rotate_x_text(30) +
+  scale_x_continuous(label=dollar_format(),breaks = round(seq(min(Annual_Inc_Clean), max(Annual_Inc_Clean), by = 50000),1))
 
 h3 = gghistogram(resp_full,x='HDI',y='..count..',
-								 bins=5,
[…]

### 2017-12-02 MSDS_CaseStudy2_Master.Rmd
Added procrastination.csv, remaining_countries.csv, and will commit again because forgot underscores

@@
 
-```{r Question3 HDI table scrape from Wikipedia}
+```{r Question3_HDI_table_scrape_from_Wikipedia}
 
@@
 
-```{r Question4 Preliminary Analysis, warning=FALSE}
+```{r Question4_Preliminary_Analysis, warning=FALSE}
 
@@
 h3 = gghistogram(resp_full,x='HDI',y='..count..',
-								 bins=35,
+								 bins=10,
 								 fill='cadetblue3',
@@
 top_jobs = match_list(resp_full$Current_Occ,findtext=keywords$title)
-
+joblist_replace = character()
 for (i in 1:length(top10Jobs$title)) {
-print(paste(tolower(as.character(top10Jobs$title[i])),'<-', unique(unique(top_jobs[[i]][,2]))))
+joblist_replace = c(joblist_replace,paste(tolower(as.character(top10Jobs$title[i])),'<-', unique(unique(top_jobs[[i]][,2]))))
 }
+write.csv(joblist_replace,'Job_Keyword_Mapping.csv')
 
@@
 sortedCC = countryCt[order(countryCt$Count, decreasing = TRUE),]
-kable(head(sortedCC,20),row.names=FALSE,format='html')%>%
+kable(head(sortedCC,19),row.names=FALSE,format='html')%>%
   kable_styling(bootstrap_options='striped',full_width=FALSE)%>%
-  row_spec(row=1:20,bold=T,color='white',background='darkred')
+  row_spec(row=1:19,bold=T,color='white',background='darkred')
+
+write.csv(sortedCC[21:length(sortedCC$Country),],'Remaining_Countries.csv')
+
 # 4E:
@@
 
-```{r Question5 Preliminary Analysis}
+```{r Question5_Preliminary_Analysis}
 
@@
 	ggtitle("Countries with the top 15 DPMean") +
-	theme(plot.title = element_text(hjust = 0.5)) +
+	theme(plot.title = element_text(hjust = 0.5),axis.text.x=element_text(angle=45,hjust=1)) +
 	xlab("Country Name")+
@@
 	ggtitle("Countries with the top 15 AIPMean") +
-	theme(plot.title = element_text(hjust = 0.5)) +
+	theme(plot.title = element_text(hjust = 0.5),axis.text.x=element_text(angle=45,hjust=1)) +
 	xlab("Country Name")+
-	ylab("AIP Mean Value")
+	ylab("AIP Mean Value")+
+  scale_x_discrete(labels=c("Dominican Republic"="Dom. Republic"))
 
@@
 
-par(mar=c(4,6,2,2))
-plot(mDFMFAvg$Annual_Inc ~ mDFMFAvg$Age, xaxt="n", yaxt="n", pch = 16, cex = 1.3, col = ifelse(mDFMFAvg$Gender == "Female", "hot pink", "blue"), xlab="", ylab="")
-axis(1,at=pretty(mDFMFAvg$Age),labels=pretty(mDFMFAvg$Age),las=1)
-axis(2,at=pretty(mDFMFAvg$Annual_Inc),labels=format(pretty(mDFMFAvg$Annual_Inc),big.mark=",", scientific=FALSE),las=1)
-mtext(text="Age", side=1, line=2)
-mtext(text="Annual Income", side=2, line=5)
-title("Mean Income by Age and Gender")
-abline(lm(mDFMFAvg$Annual_Inc ~ mDFMFAvg$Age), col = "green")
+#par(mar=c(4,6,2,2))
+# par(xpd = T, mar = par()$mar + c(0,0,0,7))
+# plot(mDFMFAvg$Annual_Inc ~ mDFMFAvg$Age, xaxt="n", yaxt="n", pch = 16, cex = 1.3, col = ifelse(mDFMFAvg$Gender == "Female", "hot pink", "blue"), xlab="", ylab="")
+# axis(1,at=pretty(mDFMFAvg$Age),labels=pretty(mDFMFAvg$Age),las=1)
+# axis(2,at=pretty(mDFMFAvg$Annual_Inc),labels=format(pretty(mDFMFAvg$Annual_Inc),big.mark=",", scientific=FALSE),las=1)
+# mtext(text="Age", side=1, line=2)
+# mtext(text="Annual Income", side=2, line=5)
+# title("Mean Income by Age and Gender")
+# abline(lm(mDFMFAvg$Annual_Inc ~ mDFMFAvg$Age), col = "green")
+# legend("topright",title="Gender",c("Male","Female"),fill=terrain.colors(3),horiz=TRUE)
+# par(mar=c(5, 4, 4, 2) + 0.1)
+
+h5 = ggscatter(mDFMFAvg,y='Annual_Inc',x='Age',
+								 color='Gender',
+								 size=2,
+								 title='Average Annual Income vs Average Age',
+								 ylab='Average Annual Income',
+								 xlab='Average Age')
+
+h5 = h5 + font('xy.text',size=12) + theme(plot.title=element_text(hjust=0.5)) +
+  scale_y_continuous(label=dollar_format(),breaks = round(seq(0, max(mDFMFAvg$Annual_Inc), by = 25000),1))
+
+h5
 
@@
 axis(2,at=pretty(mDFHDIAvg$SWLS_Avg),labels=format(pretty(mDFHDIAvg$SWLS_Avg),big.mark=",", scientific=FALSE),las=1)
-mtext(text="HDI", side=1, line=2)
+mtext(text="Mean HDI", side=1, line=2)
 mtext(text="Mean Life Satisfaction", side=2, line=5)
-title("Life Satisfaction Mean by HDI")
+title("Life Satisfaction Mean by Mean HDI")
 abline(lm(mDFHDIAvg$SWLS_Avg ~ mDFHDIAvg$HDI), col = "green")
@@
 
-ggplot(mDFHDIAvg, aes(fill=HDI_Cat, y=SWLS_Avg, x=HDI_Cat)) + 
+mDFHDIAvg$HDI_Cat_Relevel = factor(mDFHDIAvg$HDI_Cat,levels=c('Very High','High','Medium','Low'))
+
+ggplot(mDFHDIAvg, aes(fill=HDI_Cat_Relevel, y=SWLS_Avg, x=HDI_Cat_Relevel)) + 
 	scale_x_discrete(labels=c("High Human Development" = "HHD", "Very High Human Development" = "VHHD",
 														"Medium Human Development" = "MHD", "Low Human Development" = "LHD")) +
-	geom_bar(position="dodge", stat="identity") +
+	geom_bar(position="dodge", stat="identity", width=.5) +
 	ggtitle("Mean Life Satisfaction per HDI Category Test") +
@@
 	xlab("Human Development Category") +
-	ylab("Life Satisfaction Mean")
+	ylab("Mean Life Satisfaction")
 

### 2017-12-02 Code/MSDS_CaseStudy2_Master.Rmd
Initial Code Files Commit

--- 2017-12-02 MSDS_CaseStudy2_Master.Rmd
@@
 ---
-title: "MSDS Case Study 2 - Procrastination and HDI Data"
-author: "Jose Torres and Lisa Street"
+title: "Procrastination Tendencies of Company Corp. Customers"
 date: "November 29, 2017"
 output:
+  word_document: default
+  pdf_document: default
   html_document:
-    keep_md: true
+    keep_md: yes
+authors: Jose Torres and Lisa Street
 ---
+
+<br>
+
+## Introduction
+
+<br>
+
+Procrastination is broadly defined as the avoidance of performing a task that needs to be accomplished.
+The tasks in question can be of any magnitude and vary greatly in scope and impact.
+A person's self view of their own procrastination tendencies can be difficult to measure or define.
+However, over the years several procrastination scales have been developed to help shed light on the subject.
+The impact of procrastination can be great, but the sooner a person can understand their own proclivity towards task avoidance, the better the chance they have to work on these challanges.
+
+In order to gain better insight of the personal and work habits of it's customers, Company Corp.
+has asked the data scientists from Cool DS Inc to perform an analysis of the subject within it's own companies customer population.
+Since the customer count of Company Corp.
+is over 1 million, a random sample from the customer population of each country where Company Corp.
+retains a physical office, was taken.
+Each randomly assigned customer was given a survey that included questions regarding personal qualities such as age, income, marital status, etc., as well as a set of questions to be answered from four different procrastination scales.
+In addition, Cool DS Inc.
+aligned these results with the estimated Human Development Index factor for each country represented in the survey, to get a better idea of the correlation between a counties HDI and an individuals tendency to procrastinate.
+The following analysis details the findings from Cool DS Inc's study of procrastination within Company Corp.'s population.
+
+<br>
 
@@
 
-## Installing Necessary Libraries
-
-Install necessary packages if not installed:
+#### Install necessary packages if not installed:
 
@@
 
-## Load custom functions.
+#### Load custom functions created by Cool DS Inc.
 
-```{r custom functions}
+```{r custom_functions}
 
@@
 ```
+<br>
 
-## Question 2: Read in and clean raw data
+#### Gather Data for Analysis
+
+The first task performed by Cool DS Inc.
+was to survey 4,264 customers within Company Corp's universal customer population.
+The customers surveyed were taken by random sample and each customer was asked to fill out a questionaire of 61 variables.
+Some of the variables were limited in answer by drop-down, and some allowed the customer to 'write-in' their own response.
+Results of each individuals survey were tallied and consolidated into one master spreadhseet.
+Because write-in was allowed on some questions, data clean-up on the final consolidated survey was required.
+The average procrastination score across the four procrastination scales was calculated as well.
+The information below details how the data transformation and cleanup was performed.
+
+<br>
 
@@
 # 2A: Read in CSV
-filepath = 'C:\\Users\\Jose\\Downloads\\Case_Study_2\\CaseStudy2_MSDS'
+filepath = 'C:\\SMU_INTRO_TO_DS\\CASESTUDY2\\CS2\\JoseLisa\\FINAL\\Data'
 dataset_raw <- read.csv(paste(filepath,'Procrastination.csv',sep='\\'))
@@
 
-## Question 3: HDI table scrape from Wikipedia
+<br>
+
+The Human Development Index (HDI) is a summary measure of average achievement in key dimensions of human development: a long and healthy life, being knowledgeable and have a decent standard of living.
+The HDI is the geometric mean of normalized indices for each of the three dimensions.
+_(ref: United Nation's Development Program)_
+http://hdr.undp.org/en/content/human-development-index-hdi
+
+In addition to the survey, data was scraped from the Wikipedia site noted below, which assigns the 2016 estimated HDI for 2015, by country.
+This data was then merged with they survey data, by country, in order to test for correlation between procrastination and the estimated HDI factor.
+
+<br>
 
@@
 
-# Question 4: Preliminary Analysis
+<br>
+
+#### Preliminary Analysis
+
+Within the random population sample across Company Corp's offices, some of the respondents turned out to be minors.
+This was noted by any respondent with an age of 18 or under.
+Company Corp.
+advised Cool DS Inc.
+that minors should not be included in the analysis, so these respondents were removed from further review.
+This resulted in a new subset of 4,036 respondents.
+
+<br>
 
@@
 
+```
+
+<br>
+
+One of the first things we can see from a statistical analysis across our data population, are the descriptive statistics on Age, Income, HDI and the average response for the four procrastionation scales.
+Something to note is the N, or number of individuals measured in the descriptive statistic.
+For annual income this number is 3,621.
+This number is less than the 4,036 total population because some customers left this survey field empty.
+Also to note, the N for HDI is 3,844.
+This is due to some respondents not populating their county of residence within the survey.
+So when the HDI statistics were calculated, those with a country of residence of NA were not included.
+
+<br>
+
+```{r Question4_Preliminary_Analysis2, warning=FALSE}
+
 # 4B:
@@
 
-#Create 4 plots for sample figure:
+```
+
+<br>
+
+The graphs below show a histogram of Age, HDI and Annual Income across respondents.
+The boxplot chart gives shows a measure of the average of each of our procrastination scales.
+THe histogram of Age shows as for the most part, normally distributed.
+However, the HDI histogram shows as very left skewed and the histogram of Annual Income as fairly right skewed with a bit of bimodality.
+
+Also included are frequency tables to give Company Corp.
+a better idea of the population distribution of it's customer base.
+What's interesting is the high number of individuals who self-describe as procrastinators and who are also viewed as procrastinators by others.
+
+_Please note that the frequency tables for Occupation Category and Participants Per Country are rather large, so the top 10 and 20 of each table, respectively, are shown.
+For details on how the Occupation Category keywords were matched, and for a list of the Remaining Counties in the Particpants per Country list, please see the 'Job_Keyword_Mapping.csv' and 'Remaing_Countries.csv' files for details._
+
+<br>
+
+```{r Question4_Preliminary_Analysis3, warning=FALSE}
 
@@
 
-## Question 5: Visualization and Deeper Analysis
+<br>
+
+#### Deeper Analysis and Visualization
+
+A deeper analysis of the datas are also shown below.
+For several analyses, a mean value was taken to get a better perspective of the population as whole, instead of displaying unique values.
+This aides in the visualization of the variables.
+A few interesting things to note:
+
+* There are 6 countries that exist in both DP and API top 15 Means.  They are:Dominican Republic, Ecuador, Panama, Qatar, Sri Lanka   
+  and Uraguay.
+
+* As noted by the 'Average Annual Income vs Average Age' graph, there does seem to be a linear relationship between age and mean annual 	income until about age 40.
+However, starting at around age 40, an income disparity between men and women can be seen that continues   with age.
+
+* The 'Mean Life Satisfaction Mean by Mean HDI' scatterplot does not show a discernable relationship between the Satisfaction with Life
+  Scale and mean HDI factor, however, the 'Mean Life Satisfaction per HDI Category' barplot below it does signify some relationship 
+  between the Satisfaction with Life Scale and the HDI Category (Very High, High, Medium and Low), with the Low HDI Category having the   lowest SWLS average.
+
+<br>
 
@@
 	geom_bar(aes(fill=HDI_Cat), stat="identity")+
-	ggtitle("Countries with the top 15 DPMean") +
+	ggtitle("Countries with the top 15 DP Average") +
 	theme(plot.title = element_text(hjust = 0.5),axis.text.x=element_text(angle=45,hjust=1)) +
@@
 	ylab("DP Mean Value")
-
-####START HERE:
 
@@
 	geom_bar(aes(fill=HDI_Cat), stat="identity")+
-	ggtitle("Countries with the top 15 AIPMean") +
+	ggtitle("Countries with the top 15 AIP Average") +
 	theme(plot.title = element_text(hjust = 0.5),axis.text.x=element_text(angle=45,hjust=1)) +
@@
 
-# There are 6 countries that exist in both DP and API top 15 Means.  They are:
-# Dominican Republic, Ecuador, Panama, Qatar, Sri Lanka, Uraguay
-
 # 5D:
@@
 mDFMFAvg <- aggregate(Annual_Inc~Age + Gender, mDFMF, mean)
-
-#par(mar=c(4,6,2,2))
-# par(xpd = T, mar = par()$mar + c(0,0,0,7))
-# plot(mDFMFAvg$Annual_Inc ~ mDFMFAvg$Age, xaxt="n", yaxt="n", pch = 16, cex = 1.3, col = ifelse(mDFMFAvg$Gender == "Female", "hot pink", "blue"), xlab="", ylab="")
-# axis(1,at=pretty(mDFMFAvg$Age),labels=pretty(mDFMFAvg$Age),las=1)
-# axis(2,at=pretty(mDFMFAvg$Annual_Inc),labels=format(pretty(mDFMFAvg$Annual_Inc),big.mark=",", scientific=FALSE),las=1)
-# mtext(text="Age", side=1, line=2)
-# mtext(text="Annual Income", side=2, line=5)
-# title("Mean Income by Age and Gender")
-# abline(lm(mDFMFAvg$Annual_Inc ~ mDFMFAvg$Age), col = "green")
-# legend("topright",title="Gender",c("Male","Female"),fill=terrain.colors(3),horiz=TRUE)
-# par(mar=c(5, 4, 4, 2) + 0.1)
 
@@
 h5
-
-# There does seem to be a relationship between age and annual income, with annual income increasing with age.  However,
-# there also seems to be a large disparity between males and females and their annual income starting at around age 40 and 
-# growing from there.
 
@@
 mtext(text="Mean Life Satisfaction", side=2, line=5)
-title("Life Satisfaction Mean by Mean HDI")
+title("Mean Life Satisfaction Mean by Mean HDI")
 abline(lm(mDFHDIAvg$SWLS_Avg ~ mDFHDIAvg$HDI), col = "green")
@@
 	geom_bar(position="dodge", stat="identity", width=.5) +
-	ggtitle("Mean Life Satisfaction per HDI Category Test") +
+	ggtitle("Mean Life Satisfaction per HDI Category") +
 	theme(plot.title = element_text(hjust = 0.5)) +
@@
 ```
+
+<br>
+
+### Conclusion
+
+In conclusion, we are able to note several findings regarding Company Corp's customer population in terms of invidual qualities and procrastination tendencies in relation to the Human Development Index of that individuals country of residence.
+
+1.
+When assessing income, age and gender seem to matter.
+As displayed in the 'Average Annual Income vs Average Age' graph, the relationship between age and income grows in a linear fashion regardless of gender, but starting around age 40, the great income divide begins.
+We cannot infer that gender alone is the cause of this income disparity; factors such as taking time off of work to have children, etc.
+could play a role.
+However, the findings are interesting.
+
+2.
+There does seem to be a pattern among counties that procrastinate the most.
+This can be found in the 'Countries with the top 15 AIP Average' historam and the 'Countries with the top 15 DP Average' histogram, both which contain the countries of Dominican Republic, Ecuador, Panama, Qatar, Sri Lanka and Uraguay.
+And there does seem to be some correlation between the level of Procrastination with the HDI Category.
+So do Company Corp.
+customers living in countries with higher Human Develoment Indices tend to procrastinate more?
+It seems this may be the case, but further analysis may need to be performed.
+
+Since a random sample of Company Corp's customer population was taken, we can make an inference of these findings across all of Company Corp's customer population.
+An output of the details of this study can also be found in the 'Procrastination Details.pdf' file.
+
+<br>

### 2017-12-02 Code/MSDS_CaseStudy2_Master_Codebook.Rmd
Initial Code Files Commit

---
output:
  html_document:
    keep_md: true

---

# Codebook for Procrastination Tendencies of Company Corp. Customers

<br>

### Introduction

The following datasets represent a data sample collected via survey (Procrastination dataset) and a dataset scraped from Wikipedia (HDI Data) for the purposes of understanding and correlating individuals procrastination choices and views by their country of residence, with the Human Development Index factor for that country.

This data folder contains the following files:

* Procrastination.csv - a data frame containing several attributes from 4,264 individuals surveyed from from various countries, 
	and includes individual responses to difference scales of procrastination

* HDI.csv - data scraped from Wikipedia that lists, by country, the Human Development Index 2016 estimates for 2015. 	  	
  (https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index#Complete_list_of_countries)

<br>

#### Procrastination.csv:

Type: Comma-separated value file  
Dimensions: 4264 rows, 61 columns  
Unit Used: MSDS Case Study 2  
Public: Yes  
Variable Information: Individual and response variables

Summary: A data collection survey of 4264 individuals including various personal qualities and individual responses to scales of procrastination:
(AIP: Adult Inventory of Procrastination (McCown & Johnson, 1989), DP: Decisional Procrastination (Mann, 1982), 
SWLS: Satisfaction with Life Scale (Diener et al., 1985), GP: General Procrastination (Lay, 1986)). 
Details of the scales are found below.

<br>

#### Procrastination scales background:

_**AIP (Adult Inventory of Procrastination):**_

"The AIP scale measures the chronic tendency to postpone tasks in various situations (see Ferrari et al., 1995, for the complete list of items). It examines procrastination motivated by fears (e.g., success or failure), avoidance of disclosure of skill inabilities, and performance insecurity (Ferrari, 1991). The AIP assesses avoidance procrastination; that is, putting off tasks to protect one's self-esteem from possible failure. The AIP is composed of 15 Likert-scale items such that respondents express an opinion on a 5-point scale (1 = strongly disagree; 5 = strongly agree) to statements such as "I am not very good at meeting deadlines" and "I don't get things done on time." For seven items, scores are reversed so that high ratings indicate procrastination."

*(reference: Adult Inventory of Procrastination Scale (AIP): A comparison of models with an Italian sample. Available from:*
https://www.researchgate.net/publication/279532373_Adult_Inventory_of_Procrastination_Scale_AIP_A_comparison_of_models_with_an_Italian_sample)

* 1 = strongly disagree to 5 = strongly agree

_**DP (Decisional Procrastination):**_

Developed by Mann to give a reliable and valid measure of indecision.

Represented by a 5-point scale with the following scoring:

* 1 = never to 5 = always

_**SWLS (Satisfaction with Life Scale):**_

"A five item scale designed to measure global cognitive judgments of one's life satisfaction
(not a measure of either positive or negative affect). Participants indicate how much they agree or disagree with each of the 5 items using a 7-point scale that ranges from 7 strongly agree to 1 strongly disagree.""

*(reference:*
https://www.researchgate.net/file.PostFileLoader.html?id=5754d4d393553b616d2244e3&assetKey=AS%3A369794550386690%401465177299568)

* 7 - Strongly agree 
* 6 - Agree
* 5 - Slightly agree
* 4 - Neither agree nor disagree
* 3 - Slightly disagree
* 2 - Disagree
* 1 - Strongly disagree

_For this analysis, a scale of 1 through 5 was taken instead of 1 through 7._

_**GP (General Procrastination):**_

"The GPS (General Procrastination Scale) was a 20-item scale consisting of a reliability of .82 according to Cronbach's alpha coefficient."

*(reference: https://www.researchgate.net/profile/Shannon_Scielzo/publication/273259879_Finally_The_Development_and_Validation_of_the_Academic_Procrastination_Scale/links/54fcfb3d0cf20700c5e9c735/Finally-The-Development-and-Validation-of-the-Academic-Procrastination-Scale.pdf)*

* 1 point = extremely uncharacteristic.
* 2 points = moderately uncharacteristic.
* 3 points = neutral.
* 4 points = moderately characteristic.
* 5 points = extremely characteristic.

#### Procrastination.csv variables:

* Age: The participant's age in years
* Gender: The gender the participant identifes as (Male or Female)
* Kids: Binary, whether or not they have kids
* Edu: Education Level
* Work Status: What kind of job are they working
* Annual Income: All converted to dollars
* Current Occupation: A write-in for occupation
* How long have you held this position: Years: Number of years in this job
* How long have you held this position: Months: Number of months in this job
* Community: Size of community
* Country of Residence: The country where the person holds citizenship
* Marital Status: Single, Married, Divorced, Separated, etc.
* Number of sons/Number of daughters: integer number of children
* DP variables: (All numeric ratings between 1 and 5)
	+ (DP 1) I waste a lot of time on trivial matters before getting to the final decisions
	+ (DP 2) Even after I make a decision I delay acting upon it
	+ (DP 3) I don't make decisions unless I really have to
	+ (DP 4) I delay making decisions until it's too late
	+ (DP 5) I put off making decisions until it's too late
* AIP variables: (All numeric ratings between 1 and 5)	
	+ (AIP 1) I pay my bills on time
	+ (AIP 2) I am prompt and on time for most appointments.	+ (AIP 3) I lay out my clothes the night before I have an important 			appointment, so I won't be late
	+ (AIP 4) I find myself running later than I would like to be
	+ (AIP 5) I don't get things done on time
	+ (AIP 6) If someone were teaching a course on how to get things done on time, I would attend
	+ (AIP 7) My friends and family think I wait until the last minute.
	+ (AIP 8) I get important things done with time to spare
	+ (AIP 9) I am not very good at meeting deadlines
	+ (AIP 10) I find myself running out of time.
	+ (AIP 11) I schedule doctor's appointments when I am supposed to without delay
	+ (AIP 12) I am more punctual than most people I know
	+ (AIP 13) I do routine maintenance (e.g., changing the car oil) on things I own as often as I should
	+ (AIP 14) When I have to be somewhere at a certain time my friends expect me to run a bit late
	+ (AIP 15) Putting things off till the last minute has cost me money in the past
* GP Variables: (All numeric ratings between 1 and 5)
	+ (GP 1) I often find myself performing tasks that I had intended to do days before
	+ (GP 2) I often miss concerts, sporting events, or the like because I don't get around to buying tickets on time
	+ (GP 3) When planning a party, I make the necessary arrangements well in advance
	+ (GP 4) When it is time to get up in the morning, I most often get right out of bed
	+ (GP 5) A letter may sit for days after I write it before mailing it possible
	+ (GP 6) I generally return phone calls promptly
	+ (GP 7) Even jobs that require little else except sitting down and doing them, I find that they seldom get done for days
	+ (GP 8) I usually make decisions as soon as possible
	+ (GP 9) I generally delay before starting on work I have to do
	+ (GP 10) When traveling, I usually have to rush in preparing to arrive at the airport or station at the appropriate time
	+ (GP 11) When preparing to go out, I am seldom caught having to do something at the last minute
	+ (GP 12) In preparation for some deadlines, I often waste time by doing other things
	+ (GP 13) If a bill for a small amount comes, I pay it right away
	+ (GP 14) I usually return a "RSVP" request very shortly after receiving it
	+ (GP 15) I often have a task finished sooner than necessary
	+ (GP 16) I always seem to end up shopping for birthday gifts at the last minute
	+ (GP 17) I usually buy even an essential item at the last minute
	+ (GP 18) I usually accomplish all the things I plan to do in a day
	+ (GP 19) I am continually saying "I'll do it tomorrow"
	+ (GP 20) I usually take care of all the tasks I have to do before I settle down and relax for the evening
* SWLS Variables: (All numeric ratings between 0 and 5)	
	+ (SWLS 1) In most ways my life is close to my ideal
	+ (SWLS 2)The conditions of my life are excellent
	+ (SWLS 3) I am satisfied with my life
	+ (SWLS 4) So far I have gotten the important things I want in life
	+ (SWLS 5) If I could live my life over, I would change almost nothing
* Do you consider yourself a procrastinator: a binary response
* Do others consider you a procrastinator: a binary response

<br>

#### HDI.csv:

Type: Comma-separated value file  
Dimensions: 189 rows, 2 columns  
Unit Used: MSDS Case Study 2  
Public: Yes  
Variable Information: Country and 2016 HDI estimates for 2015

Summary: HDI Dataset: A list of all countries by the HDI (Human Development Index) as included in the United Nations Development Programme's Human Development Report. The data from this site was scraped and pushed into a CSV file, to later merge with the Procrastination dataset listed above, by country.
(ref: Wikipedia)

<br>

#### HDI.csv variables:

1. Country: Name of the country from the UN's Development Programme's Human Development Report
2. HDI: 2016 Human Development Index score estimate for 2015

<br>

### 2017-12-02 Code/MSDS_CaseStudy2_Master.Rmd
Upload new Master RMD, MD and HTML

@@
 output:
-  word_document: default
-  pdf_document: default
   html_document:
-    keep_md: yes
+    keep_md: true
 authors: Jose Torres and Lisa Street
@@
 
-```{r Question4_Preliminary_Analysis2, warning=FALSE}
+```{r Question4_Preliminary_Analysis2, warning=FALSE,echo=TRUE}
 
@@
 
-```{r Question4_Preliminary_Analysis3, warning=FALSE}
+```{r Question4_Preliminary_Analysis3, warning=FALSE,echo=TRUE}
 
@@
 
-```{r Question5_Preliminary_Analysis}
+```{r Question5_Preliminary_Analysis,echo=TRUE}
 

### 2017-12-02 MSDS_CaseStudy2_Master.Rmd
test commit

@@
 ---
-title: "MSDS Case Study 2 - Procrastination and HDI Data"
-author: "Jose Torres and Lisa Street"
+title: "Procrastination Tendencies of Company Corp. Customers"
 date: "November 29, 2017"
@@
     keep_md: true
+authors: Jose Torres and Lisa Street
 ---
+
+<br>
+
+## Introduction
+
+<br>
+
+Procrastination is broadly defined as the avoidance of performing a task that needs to be accomplished.
+The tasks in question can be of any magnitude and vary greatly in scope and impact.
+A person's self view of their own procrastination tendencies can be difficult to measure or define.
+However, over the years several procrastination scales have been developed to help shed light on the subject.
+The impact of procrastination can be great, but the sooner a person can understand their own proclivity towards task avoidance, the better the chance they have to work on these challanges.
+
+In order to gain better insight of the personal and work habits of it's customers, Company Corp.
+has asked the data scientists from Cool DS Inc to perform an analysis of the subject within it's own companies customer population.
+Since the customer count of Company Corp.
+is over 1 million, a random sample from the customer population of each country where Company Corp.
+retains a physical office, was taken.
+Each randomly assigned customer was given a survey that included questions regarding personal qualities such as age, income, marital status, etc., as well as a set of questions to be answered from four different procrastination scales.
+In addition, Cool DS Inc.
+aligned these results with the estimated Human Development Index factor for each country represented in the survey, to get a better idea of the correlation between a counties HDI and an individuals tendency to procrastinate.
+The following analysis details the findings from Cool DS Inc's study of procrastination within Company Corp.'s population.
+
+<br>
 
@@
 ```
+<br>
 
-## Question 2: Read in and clean raw data
+#### Gather Data for Analysis
 
-```{r Question2}
+The first task performed by Cool DS Inc.
+was to survey 4,264 customers within Company Corp's universal customer population.
+The customers surveyed were taken by random sample and each customer was asked to fill out a questionaire of 61 variables.
+Some of the variables were limited in answer by drop-down, and some allowed the customer to 'write-in' their own response.
+Results of each individuals survey were tallied and consolidated into one master spreadhseet.
+Because write-in was allowed on some questions, data clean-up on the final consolidated survey was required.
+The average procrastination score across the four procrastination scales was calculated as well.
+The information below details how the data transformation and cleanup was performed.
+
+<br>
+
+```{r, Question2}
 
@@
 
-## Question 3: HDI table scrape from Wikipedia
+<br>
 
-```{r Question3_HDI_table_scrape_from_Wikipedia}
+The Human Development Index (HDI) is a summary measure of average achievement in key dimensions of human development: a long and healthy life, being knowledgeable and have a decent standard of living.
+The HDI is the geometric mean of normalized indices for each of the three dimensions.
+_(ref: United Nation's Development Program)_
+http://hdr.undp.org/en/content/human-development-index-hdi
+
+In addition to the survey, data was scraped from the Wikipedia site noted below, which assigns the 2016 estimated HDI for 2015, by country.
+This data was then merged with they survey data, by country, in order to test for correlation between procrastination and the estimated HDI factor.
+
+<br>
+
+```{r, Question3_HDI_table_scrape_from_Wikipedia}
 
@@
 
-# Question 4: Preliminary Analysis
+<br>
 
-```{r Question4_Preliminary_Analysis, warning=FALSE}
+#### Preliminary Analysis
+
+Within the random population sample across Company Corp's offices, some of the respondents turned out to be minors.
+This was noted by any respondent with an age of 18 or under.
+Company Corp.
+advised Cool DS Inc.
+that minors should not be included in the analysis, so these respondents were removed from further review.
+This resulted in a new subset of 4,036 respondents.
+
+<br>
+
+```{r, Question4_Preliminary_Analysis, warning=FALSE}
 
@@
 
+```
+
+<br>
+
+One of the first things we can see from a statistical analysis across our data population, are the descriptive statistics on Age, Income, HDI and the average response for the four procrastionation scales.
+Something to note is the N, or number of individuals measured in the descriptive statistic.
+For annual income this number is 3,621.
+This number is less than the 4,036 total population because some customers left this survey field empty.
+Also to note, the N for HDI is 3,844.
+This is due to some respondents not populating their county of residence within the survey.
+So when the HDI statistics were calculated, those with a country of residence of NA were not included.
+
+<br>
+
+```{r, Question4_Preliminary_Analysis2, warning=FALSE,echo=TRUE}
+
 # 4B:
@@
 
-#Create 4 plots for sample figure:
+```
+
+<br>
+
+The graphs below show a histogram of Age, HDI and Annual Income across respondents.
+The boxplot chart gives shows a measure of the average of each of our procrastination scales.
+THe histogram of Age shows as for the most part, normally distributed.
+However, the HDI histogram shows as very left skewed and the histogram of Annual Income as fairly right skewed with a bit of bimodality.
+
+Also included are frequency tables to give Company Corp.
+a better idea of the population distribution of it's customer base.
+What's interesting is the high number of individuals who self-describe as procrastinators and who are also viewed as procrastinators by others.
+
+_Please note that the frequency tables for Occupation Category and Participants Per Country are rather large, so the top 10 and 20 of each table, respectively, are shown.
+For details on how the Occupation Category keywords were matched, and for a list of the Remaining Counties in the Particpants per Country list, please see the 'Job_Keyword_Mapping.csv' and 'Remaing_Countries.csv' files for details._
+
+<br>
+
+```{r, Question4_Preliminary_Analysis3, warning=FALSE,echo=TRUE}
 
@@
 
-## Question 5: Visualization and Deeper Analysis
+<br>
 
-```{r Question5_Preliminary_Analysis}
+#### Deeper Analysis and Visualization
+
+A deeper analysis of the datas are also shown below.
+For several analyses, a mean value was taken to get a better perspective of the population as whole, instead of displaying unique values.
+This aides in the visualization of the variables.
+A few interesting things to note:
+
+* There are 6 countries that exist in both DP and API top 15 Means.  They are:Dominican Republic, Ecuador, Panama, Qatar, Sri Lanka   
+  and Uraguay.
+
+* As noted by the 'Average Annual Income vs Average Age' graph, there does seem to be a linear relationship between age and mean annual 	income until about age 40.
+However, starting at around age 40, an income disparity between men and women can be seen that continues   with age.
+
+* The 'Mean Life Satisfaction Mean by Mean HDI' scatterplot does not show a discernable relationship between the Satisfaction with Life
+  Scale and mean HDI factor, however, the 'Mean Life Satisfaction per HDI Category' barplot below it does signify some relationship 
+  between the Satisfaction with Life Scale and the HDI Category (Very High, High, Medium and Low), with the Low HDI Category having the   lowest SWLS average.
+
+<br>
+
+```{r, Question5_Preliminary_Analysis,echo=TRUE}
 

### 2017-12-03 Code/MSDS_CaseStudy2_Master.Rmd
Re-commit RMD, HTML and MD updated files
Updated spelling and punctuation issues.

@@
 
-In order to gain better insight of the personal and work habits of it's customers, Company Corp.
-has asked the data scientists from Cool DS Inc to perform an analysis of the subject within it's own companies customer population.
+In order to gain better insight of the personal and work habits of its customers, Company Corp.
+has asked the data scientists from Cool DS Inc to perform an analysis of the subject within its own companies customer population.
 Since the customer count of Company Corp.
@@
 retains a physical office, was taken.
-Each randomly assigned customer was given a survey that included questions regarding personal qualities such as age, income, marital status, etc., as well as a set of questions to be answered from four different procrastination scales.
+Each randomly assigned customer was given a survey that included questions regarding personal qualities such as age, income, marital status, etc., as well as a set of questions to be answered from four different procrastination scales (_see MSDS_CaseStudy2_Master_Codebook.MD for procrastination scale details_).
 In addition, Cool DS Inc.
-aligned these results with the estimated Human Development Index factor for each country represented in the survey, to get a better idea of the correlation between a counties HDI and an individuals tendency to procrastinate.
+aligned these results with the estimated Human Development Index factor for each country represented in the survey, to get a better idea of the correlation between a countries HDI and an individuals tendency to procrastinate.
 The following analysis details the findings from Cool DS Inc's study of procrastination within Company Corp.'s population.
@@
 was to survey 4,264 customers within Company Corp's universal customer population.
-The customers surveyed were taken by random sample and each customer was asked to fill out a questionaire of 61 variables.
-Some of the variables were limited in answer by drop-down, and some allowed the customer to 'write-in' their own response.
+The customers surveyed were taken by random sample and each customer was asked to fill out a questionaire consisting of 61 questions related to personal and procrastiation scale questions.
+Some of the questions were limited in answer by drop-down, and some allowed the customer to 'write-in' their own response.
 Results of each individuals survey were tallied and consolidated into one master spreadhseet.
@@
 
-```{r Question2}
+```{r, Question2}
 
@@
 
-The Human Development Index (HDI) is a summary measure of average achievement in key dimensions of human development: a long and healthy life, being knowledgeable and have a decent standard of living.
-The HDI is the geometric mean of normalized indices for each of the three dimensions.
+"The Human Development Index (HDI) is a summary measure of average achievement in key dimensions of human development: a long and healthy life, being knowledgeable and have a decent standard of living.
+The HDI is the geometric mean of normalized indices for each of the three dimensions".
 _(ref: United Nation's Development Program)_
@@
 
-In addition to the survey, data was scraped from the Wikipedia site noted below, which assigns the 2016 estimated HDI for 2015, by country.
+In addition to the survey, data was scraped from the UN's HDI Wikipedia site noted in the code snippit below, which assigns the 2016 estimated HDI for 2015, by country.
 This data was then merged with they survey data, by country, in order to test for correlation between procrastination and the estimated HDI factor.
@@
 
-```{r Question3_HDI_table_scrape_from_Wikipedia}
+```{r, Question3_HDI_table_scrape_from_Wikipedia}
 
@@
 
-Within the random population sample across Company Corp's offices, some of the respondents turned out to be minors.
-This was noted by any respondent with an age of 18 or under.
+Within the random sample population, some of the respondents turned out to be minors.
+This was noted by any respondent with an age of under 18.
 Company Corp.
@@
 
-```{r Question4_Preliminary_Analysis, warning=FALSE}
+```{r, Question4_Preliminary_Analysis, warning=FALSE}
 
@@
 
-One of the first things we can see from a statistical analysis across our data population, are the descriptive statistics on Age, Income, HDI and the average response for the four procrastionation scales.
+One of the first things found from a statistical analysis across the data population, are the descriptive statistics on Age, Income, HDI and the average response for the four procrastionation scales.
 Something to note is the N, or number of individuals measured in the descriptive statistic.
 For annual income this number is 3,621.
-This number is less than the 4,036 total population because some customers left this survey field empty.
+This number is less than the 4,036 total population because some customers left the annual income survey field empty.
 Also to note, the N for HDI is 3,844.
@@
 
-```{r Question4_Preliminary_Analysis2, warning=FALSE,echo=TRUE}
+```{r, Question4_Preliminary_Analysis2, warning=FALSE,echo=TRUE}
 
@@
 The graphs below show a histogram of Age, HDI and Annual Income across respondents.
-The boxplot chart gives shows a measure of the average of each of our procrastination scales.
-THe histogram of Age shows as for the most part, normally distributed.
+The boxplot chart gives a measure of the average of each of our procrastination scales.
+The histogram of Age shows for the most part as normally distributed.
 However, the HDI histogram shows as very left skewed and the histogram of Annual Income as fairly right skewed with a bit of bimodality.
 
-Also included are frequency tables to give Company Corp.
-a better idea of the population distribution of it's customer base.
-What's interesting is the high number of individuals who self-describe as procrastinators and who are also viewed as procrastinators by others.
+Also included are frequency tables that provide Company Corp.
+with a better idea of the population distribution of its customer base.
+What's interesting is the high number of individuals who self-describe as procrastinators and those who are also viewed as procrastinators by others.
 
-_Please note that the frequency tables for Occupation Category and Participants Per Country are rather large, so the top 10 and 20 of each table, respectively, are shown.
+_Please note that the frequency tables for Occupation Category and Participants Per Country are rather large, so the top 10 and 20 of each table, are displayed.
 For details on how the Occupation Category keywords were matched, and for a list of the Remaining Counties in the Particpants per Country list, please see the 'Job_Keyword_Mapping.csv' and 'Remaing_Countries.csv' files for details._
@@
 
-```{r Question4_Preliminary_Analysis3, warning=FALSE,echo=TRUE}
+```{r, Question4_Preliminary_Analysis3, warning=FALSE,echo=TRUE}
 
@@
 					ncol=2)
-
-# Neither the Age nor Annual Income histograms are particularly normally distributed.  The Age histogram is a bit of a bimodal
-# distribution with peaks around the ages of 25, 45 and 55. THe Annual Income is more right-skewed.
 
@@
 
-A deeper analysis of the datas are also shown below.
-For several analyses, a mean value was taken to get a better perspective of the population as whole, instead of displaying unique values.
+A deeper analysis of the data are also shown below.
+For several analyses, a mean value was taken in order to provide a cleaner perspective of the population as whole, instead of displaying unique values.
 This aides in the visualization of the variables.
@@
 
-* There are 6 countries that exist in both DP and API top 15 Means.  They are:Dominican Republic, Ecuador, Panama, Qatar, Sri Lanka   
-  and Uraguay.
+* There are 6 countries that exist in both the DP and AIP top 15 Means. They are:Dominican Republic, Ecuador, Panama, Qatar, Sri Lanka   and Uraguay.
 
 * As noted by the 'Average Annual Income vs Average Age' graph, there does seem to be a linear relationship between age and mean annual 	income until about age 40.
-However, starting at around age 40, an income disparity between men and women can be seen that continues   with age.
+However, starting at around age 40, an income disparity between men and women can be seen that continues   with age progression.
 
 * The 'Mean Life Satisfaction Mean by Mean HDI' scatterplot does not show a discernable relationship between the Satisfaction with Life
-  Scale and mean HDI factor, however, the 'Mean Life Satisfaction per HDI Category' barplot below it does signify some relationship 
+  Scale and mean HDI factor. However, the 'Mean Life Satisfaction per HDI Category' barplot does signify some relationship 
   between the Satisfaction with Life Scale and the HDI Category (Very High, High, Medium and Low), with the Low HDI Category having the   lowest SWLS average.
@@
 
-```{r Question5_Preliminary_Analysis,echo=TRUE}
+```{r, Question5_Preliminary_Analysis,echo=TRUE}
 
@@
 When assessing income, age and gender seem to matter.
-As displayed in the 'Average Annual Income vs Average Age' graph, the relationship between age and income grows in a linear fashion regardless of gender, but starting around age 40, the great income divide begins.
-We cannot infer that gender alone is the cause of this income disparity; factors such as taking time off of work to have children, etc.
+As displayed in the 'Average Annual Income vs Average Age' graph, the relationship between age and income grows in a linear fashion regardless of gender, but beginning around age 40, the great income divide begins.
+We cannot infer that gender alone is the cause of this income disparity, factors such as taking time off of work to raise children, etc.
 could play a role.
@@
 2.
-There does seem to be a pattern among counties that procrastinate the most.
+There does seem to be a pattern among countries that procrastinate the most.
 This can be found in the 'Countries with the top 15 AIP Average' historam and the 'Countries with the top 15 DP Average' histogram, both which contain the countries of Dominican Republic, Ecuador, Panama, Qatar, Sri Lanka and Uraguay.
-And there does seem to be some correlation between the level of Procrastination with the HDI Category.
+Also, there does seem to be some correlation between the level of Procrastination with the HDI Category.
 So do Company Corp.
